Towards Practical First-Order Model Counting

### 2025-06-05 doc/paper/plot.tex
Potentially the final (camera-ready) version

% Created by tikzDevice version 0.12.6 on 2025-01-24 14:00:20
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 37.91, 89.74) --
	( 41.73, 84.24) --
	( 45.54, 84.24) --
	( 49.36, 84.34) --
	( 53.17, 87.56) --
	( 56.99,109.01);
\definecolor{drawColor}{RGB}{117,112,179}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] ( 37.91, 81.38) --
	( 41.73, 81.38) --
	( 45.54, 81.38) --
	( 49.36, 81.38) --
	( 53.17, 81.38) --
	( 56.99, 81.38) --
	( 60.80, 81.39) --
	( 64.62, 81.41) --
	( 68.43, 81.49) --
	( 72.24, 81.81) --
	( 76.06, 83.15) --
	( 79.87, 87.02);
\definecolor{fillColor}{RGB}{117,112,179}

\path[fill=fillColor] ( 35.95, 79.42) --
	( 39.87, 79.42) --
	( 39.87, 83.35) --
	( 35.95, 83.35) --
	cycle;

\path[fill=fillColor] ( 39.77, 79.42) --
	( 43.69, 79.42) --
	( 43.69, 83.35) --
	( 39.77, 83.35) --
	cycle;

\path[fill=fillColor] ( 43.58, 79.42) --
	( 47.50, 79.42) --
	( 47.50, 83.35) --
	( 43.58, 83.35) --
	cycle;

\path[fill=fillColor] ( 47.39, 79.42) --
	( 51.32, 79.42) --
	( 51.32, 83.35) --
	( 47.39, 83.35) --
	cycle;

\path[fill=fillColor] ( 51.21, 79.42) --
	( 55.13, 79.42) --
	( 55.13, 83.35) --
	( 51.21, 83.35) --
	cycle;

\path[fill=fillColor] ( 55.02, 79.42) --
	( 58.95, 79.42) --
	( 58.95, 83.35) --
	( 55.02, 83.35) --
	cycle;

\path[fill=fillColor] ( 58.84, 79.43) --
	( 62.76, 79.43) --
	( 62.76, 83.35) --
	( 58.84, 83.35) --
	cycle;

\path[fill=fillColor] ( 62.65, 79.45) --
	( 66.58, 79.45) --
	( 66.58, 83.37) --
	( 62.65, 83.37) --
	cycle;

\path[fill=fillColor] ( 66.47, 79.53) --
	( 70.39, 79.53) --
	( 70.39, 83.45) --
	( 66.47, 83.45) --
	cycle;

\path[fill=fillColor] ( 70.28, 79.84) --
	( 74.21, 79.84) --
	( 74.21, 83.77) --
	( 70.28, 83.77) --
	cycle;

\path[fill=fillColor] ( 74.10, 81.19) --
	( 78.02, 81.19) --
	( 78.02, 85.11) --
	( 74.10, 85.11) --
	cycle;

\path[fill=fillColor] ( 77.91, 85.05) --
	( 81.84, 85.05) --
	( 81.84, 88.98) --
	( 77.91, 88.98) --
	cycle;
\definecolor{fillColor}{RGB}{27,158,119}

\path[fill=fillColor] ( 37.91, 89.74) circle (  1.96);

\path[fill=fillColor] ( 41.73, 84.24) circle (  1.96);

\path[fill=fillColor] ( 45.54, 84.24) circle (  1.96);

\path[fill=fillColor] ( 49.36, 84.34) circle (  1.96);

\path[fill=fillColor] ( 53.17, 87.56) circle (  1.96);

\path[fill=fillColor] ( 56.99,109.01) circle (  1.96);
\definecolor{drawColor}{gray}{0.70}

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] (147.31, 84.74) --
	(151.13, 84.06) --
	(154.94, 83.93) --
	(158.76, 83.97) --
	(162.57, 84.20) --
	(166.39, 84.27) --
	(170.20, 84.38) --
	(174.02, 86.20) --
	(177.83, 93.38) --
	(181.65,111.72);
\definecolor{drawColor}{RGB}{217,95,2}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (147.31, 62.86) --
	(151.13, 60.69) --
	(154.94, 60.69) --
	(158.76, 60.69);
\definecolor{drawColor}{RGB}{117,112,179}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (147.31, 72.23) --
	(151.13, 72.23) --
	(154.94, 72.23) --
	(158.76, 72.23) --
	(162.57, 72.23) --
	(166.39, 72.23) --
	(170.20, 72.23) --
	(174.02, 72.27) --
	(177.83, 72.70) --
	(181.65, 76.95) --
	(185.46, 89.66) --
	(189.28,106.37) --
	(193.09,123.35);
\definecolor{drawColor}{RGB}{231,41,138}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (147.31, 72.11) --
	(151.13, 72.11) --
	(154.94, 72.11) --
	(158.76, 72.11) --
	(162.57, 72.11) --
	(166.39, 72.11) --
	(170.20, 72.11) --
	(174.02, 72.15) --
	(177.83, 72.59) --
	(181.65, 76.89) --
	(185.46, 89.67) --
	(189.28,106.37) --
	(193.09,123.35);
\definecolor{fillColor}{RGB}{27,158,119}

\path[fill=fillColor] (147.31, 84.74) circle (  1.96);

\path[fill=fillColor] (151.13, 84.06) circle (  1.96);

\path[fill=fillColor] (154.94, 83.93) circle (  1.96);

\path[fill=fillColor] (158.76, 83.97) circle (  1.96);

\path[fill=fillColor] (162.57, 84.20) circle (  1.96);

\path[fill=fillColor] (166.39, 84.27) circle (  1.96);

\path[fill=fillColor] (170.20, 84.38) circle (  1.96);

\path[fill=fillColor] (174.02, 86.20) circle (  1.96);

\path[fill=fillColor] (177.83, 93.38) circle (  1.96);

\path[fill=fillColor] (181.65,111.72) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (144.54, 72.11) -- (150.09, 72.11);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (147.31, 69.34) -- (147.31, 74.89);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (148.35, 72.11) -- (153.90, 72.11);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (151.13, 69.33) -- (151.13, 74.88);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (152.17, 72.11) -- (157.72, 72.11);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (154.94, 69.33) -- (154.94, 74.88);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (155.98, 72.11) -- (161.53, 72.11);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (158.76, 69.33) -- (158.76, 74.88);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (159.80, 72.11) -- (165.35, 72.11);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (162.57, 69.33) -- (162.57, 74.88);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (163.61, 72.11) -- (169.16, 72.11);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (166.39, 69.33) -- (166.39, 74.88);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (167.43, 72.11) -- (172.98, 72.11);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (170.20, 69.34) -- (170.20, 74.89);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (171.24, 72.15) -- (176.79, 72.15);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (174.02, 69.37) -- (174.02, 74.92);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (175.06, 72.59) -- (180.61, 72.59);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (177.83, 69.81) -- (177.83, 75.36);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (178.87, 76.89) -- (184.42, 76.89);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (181.65, 74.12) -- (181.65, 79.67);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (182.69, 89.67) -- (188.24, 89.67);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (185.46, 86.90) -- (185.46, 92.45);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (186.50,106.37) -- (192.05,106.37);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (189.28,103.59) -- (189.28,109.14);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (190.32,123.35) -- (195.86,123.35);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (193.09,120.57) -- (193.09,126.12);
\definecolor{fillColor}{RGB}{217,95,2}

\path[fill=fillColor] (147.31, 65.91) --
	(149.96, 61.33) --
	(144.67, 61.33) --
	cycle;

\path[fill=fillColor] (151.13, 63.74) --
	(153.77, 59.17) --
	(148.49, 59.17) --
	cycle;

\path[fill=fillColor] (154.94, 63.74) --
	(157.59, 59.17) --
	(152.30, 59.17) --
	cycle;

\path[fill=fillColor] (158.76, 63.74) --
	(161.40, 59.17) --
	(156.12, 59.17) --
	cycle;
\definecolor{fillColor}{RGB}{117,112,179}

\path[fill=fillColor] (145.35, 70.27) --
	(149.28, 70.27) --
	(149.28, 74.20) --
	(145.35, 74.20) --
	cycle;

\path[fill=fillColor] (149.17, 70.27) --
	(153.09, 70.27) --
	(153.09, 74.19) --
	(149.17, 74.19) --
	cycle;

\path[fill=fillColor] (152.98, 70.27) --
	(156.91, 70.27) --
	(156.91, 74.19) --
	(152.98, 74.19) --
	cycle;

\path[fill=fillColor] (156.80, 70.27) --
	(160.72, 70.27) --
	(160.72, 74.19) --
	(156.80, 74.19) --
	cycle;

\path[fill=fillColor] (160.61, 70.27) --
	(164.54, 70.27) --
	(164.54, 74.19) --
	(160.61, 74.19) --
	cycle;

\path[fill=fillColor] (164.43, 70.27) --
	(168.35, 70.27) --
	(168.35, 74.19) --
	(164.43, 74.19) --
	cycle;

\path[fill=fillColor] (168.24, 70.27) --
	(172.16, 70.27) --
	(172.16, 74.20) --
	(168.24, 74.20) --
	cycle;

\path[fill=fillColor] (172.05, 70.31) --
	(175.98, 70.31) --
	(175.98, 74.23) --
	(172.05, 74.23) --
	cycle;

\path[fill=fillColor] (175.87, 70.74) --
	(179.79, 70.74) --
	(179.79, 74.66) --
	(175.87, 74.66) --
	cycle;

\path[fill=fillColor] (179.68, 74.99) --
	(183.61, 74.99) --
	(183.61, 78.91) --
	(179.68, 78.91) --
	cycle;

\path[fill=fillColor] (183.50, 87.70) --
	(187.42, 87.70) --
	(187.42, 91.62) --
	(183.50, 91.62) --
	cycle;

\path[fill=fillColor] (187.31,104.41) --
	(191.24,104.41) --
	(191.24,108.33) --
	(187.31,108.33) --
	cycle;

\path[fill=fillColor] (191.13,121.39) --
	(195.05,121.39) --
	(195.05,125.31) --
	(191.13,125.31) --
	cycle;
\definecolor{drawColor}{gray}{0.70}

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] (256.72, 85.43) --
	(260.53, 83.72) --
	(264.35, 83.89) --
	(268.16, 83.69) --
	(271.97, 85.93) --
	(275.79,108.62);
\definecolor{drawColor}{RGB}{217,95,2}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (256.72, 61.86) --
	(260.53, 61.00) --
	(264.35, 61.00) --
	(268.16, 61.00) --
	(271.97, 61.00) --
	(275.79, 61.15) --
	(279.60, 61.15);
\definecolor{drawColor}{RGB}{117,112,179}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (256.72, 73.16) --
	(260.53, 73.16) --
	(264.35, 73.16) --
	(268.16, 73.16) --
	(271.97, 73.16) --
	(275.79, 73.16) --
	(279.60, 73.16) --
	(283.42, 73.16) --
	(287.23, 73.16) --
	(291.05, 73.16) --
	(294.86, 73.16) --
	(298.68, 73.16) --
	(302.49, 73.17) --
	(306.31, 73.17) --
	(310.12, 73.20) --
	(313.94, 73.25) --
	(317.75, 73.38) --
	(321.56, 73.71) --
	(325.38, 74.42) --
	(329.19, 76.07) --
	(333.01, 78.80) --
	(336.82, 82.57) --
	(340.64, 87.78) --
	(344.45, 94.24) --
	(348.27,100.04) --
	(352.08,106.25);
\definecolor{drawColor}{RGB}{231,41,138}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (256.72, 72.63) --
	(260.53, 72.63) --
	(264.35, 72.63) --
	(268.16, 72.63) --
	(271.97, 72.63) --
	(275.79, 72.63) --
	(279.60, 72.63) --
	(283.42, 72.63) --
	(287.23, 72.63) --
	(291.05, 72.63) --
	(294.86, 72.63) --
	(298.68, 72.63) --
	(302.49, 72.64) --
	(306.31, 72.64) --
	(310.12, 72.67) --
	(313.94, 72.73) --
	(317.75, 72.87) --
	(321.56, 73.21) --
	(325.38, 73.96) --
	(329.19, 75.58) --
	(333.01, 78.49) --
	(336.82, 82.32) --
	(340.64, 87.62) --
	(344.45, 94.08) --
	(348.27, 99.98) --
	(352.08,106.31);
\definecolor{fillColor}{RGB}{117,112,179}

\path[fill=fillColor] (254.75, 71.20) --
	(258.68, 71.20) --
	(258.68, 75.12) --
	(254.75, 75.12) --
	cycle;

\path[fill=fillColor] (258.57, 71.20) --
	(262.49, 71.20) --
	(262.49, 75.12) --
	(258.57, 75.12) --
	cycle;

\path[fill=fillColor] (262.38, 71.20) --
	(266.31, 71.20) --
	(266.31, 75.12) --
	(262.38, 75.12) --
	cycle;

\path[fill=fillColor] (266.20, 71.20) --
	(270.12, 71.20) --
	(270.12, 75.12) --
	(266.20, 75.12) --
	cycle;

\path[fill=fillColor] (270.01, 71.20) --
	(273.94, 71.20) --
	(273.94, 75.12) --
	(270.01, 75.12) --
	cycle;

\path[fill=fillColor] (273.83, 71.20) --
	(277.75, 71.20) --
	(277.75, 75.12) --
	(273.83, 75.12) --
	cycle;

\path[fill=fillColor] (277.64, 71.20) --
	(281.57, 71.20) --
	(281.57, 75.12) --
	(277.64, 75.12) --
	cycle;

\path[fill=fillColor] (281.46, 71.20) --
	(285.38, 71.20) --
	(285.38, 75.12) --
	(281.46, 75.12) --
	cycle;

\path[fill=fillColor] (285.27, 71.20) --
	(289.20, 71.20) --
	(289.20, 75.12) --
	(285.27, 75.12) --
	cycle;

\path[fill=fillColor] (289.09, 71.20) --
	(293.01, 71.20) --
	(293.01, 75.12) --
	(289.09, 75.12) --
	cycle;

\path[fill=fillColor] (292.90, 71.20) --
	(296.82, 71.20) --
	(296.82, 75.12) --
	(292.90, 75.12) --
	cycle;

\path[fill=fillColor] (296.72, 71.20) --
	(300.64, 71.20) --
	(300.64, 75.12) --
	(296.72, 75.12) --
	cycle;

\path[fill=fillColor] (300.53, 71.21) --
	(304.45, 71.21) --
	(304.45, 75.13) --
	(300.53, 75.13) --
	cycle;

\path[fill=fillColor] (304.34, 71.21) --
	(308.27, 71.21) --
	(308.27, 75.14) --
	(304.34, 75.14) --
	cycle;

\path[fill=fillColor] (308.16, 71.24) --
	(312.08, 71.24) --
	(312.08, 75.16) --
	(308.16, 75.16) --
	cycle;

\path[fill=fillColor] (311.97, 71.29) --
	(315.90, 71.29) --
	(315.90, 75.22) --
	(311.97, 75.22) --
	cycle;

\path[fill=fillColor] (315.79, 71.42) --
	(319.71, 71.42) --
	(319.71, 75.35) --
	(315.79, 75.35) --
	cycle;

\path[fill=fillColor] (319.60, 71.75) --
	(323.53, 71.75) --
	(323.53, 75.67) --
	(319.60, 75.67) --
	cycle;

\path[fill=fillColor] (323.42, 72.46) --
	(327.34, 72.46) --
	(327.34, 76.39) --
	(323.42, 76.39) --
	cycle;

\path[fill=fillColor] (327.23, 74.10) --
	(331.16, 74.10) --
	(331.16, 78.03) --
	(327.23, 78.03) --
	cycle;

\path[fill=fillColor] (331.05, 76.84) --
	(334.97, 76.84) --
	(334.97, 80.76) --
	(331.05, 80.76) --
	cycle;

\path[fill=fillColor] (334.86, 80.61) --
	(338.79, 80.61) --
	(338.79, 84.53) --
	(334.86, 84.53) --
	cycle;

\path[fill=fillColor] (338.68, 85.82) --
	(342.60, 85.82) --
	(342.60, 89.74) --
	(338.68, 89.74) --
	cycle;

\path[fill=fillColor] (342.49, 92.28) --
	(346.41, 92.28) --
	(346.41, 96.20) --
	(342.49, 96.20) --
	cycle;

>>>>

% Created by tikzDevice version 0.12.6 on 2025-06-03 07:37:32
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 37.91, 81.38) --
	( 41.73, 81.38) --
	( 45.54, 81.38) --
	( 49.36, 81.38) --
	( 53.17, 81.38) --
	( 56.99, 81.38) --
	( 60.80, 81.39) --
	( 64.62, 81.41) --
	( 68.43, 81.49) --
	( 72.24, 81.81) --
	( 76.06, 83.15) --
	( 79.87, 87.02);
\definecolor{drawColor}{RGB}{117,112,179}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] ( 37.91, 89.74) --
	( 41.73, 84.24) --
	( 45.54, 84.24) --
	( 49.36, 84.34) --
	( 53.17, 87.56) --
	( 56.99,109.01);
\definecolor{fillColor}{RGB}{27,158,119}

\path[fill=fillColor] ( 37.91, 81.38) circle (  1.96);

\path[fill=fillColor] ( 41.73, 81.38) circle (  1.96);

\path[fill=fillColor] ( 45.54, 81.38) circle (  1.96);

\path[fill=fillColor] ( 49.36, 81.38) circle (  1.96);

\path[fill=fillColor] ( 53.17, 81.38) circle (  1.96);

\path[fill=fillColor] ( 56.99, 81.38) circle (  1.96);

\path[fill=fillColor] ( 60.80, 81.39) circle (  1.96);

\path[fill=fillColor] ( 64.62, 81.41) circle (  1.96);

\path[fill=fillColor] ( 68.43, 81.49) circle (  1.96);

\path[fill=fillColor] ( 72.24, 81.81) circle (  1.96);

\path[fill=fillColor] ( 76.06, 83.15) circle (  1.96);

\path[fill=fillColor] ( 79.87, 87.02) circle (  1.96);
\definecolor{fillColor}{RGB}{117,112,179}

\path[fill=fillColor] ( 35.95, 87.78) --
	( 39.87, 87.78) --
	( 39.87, 91.70) --
	( 35.95, 91.70) --
	cycle;

\path[fill=fillColor] ( 39.77, 82.28) --
	( 43.69, 82.28) --
	( 43.69, 86.20) --
	( 39.77, 86.20) --
	cycle;

\path[fill=fillColor] ( 43.58, 82.28) --
	( 47.50, 82.28) --
	( 47.50, 86.20) --
	( 43.58, 86.20) --
	cycle;

\path[fill=fillColor] ( 47.39, 82.38) --
	( 51.32, 82.38) --
	( 51.32, 86.30) --
	( 47.39, 86.30) --
	cycle;

\path[fill=fillColor] ( 51.21, 85.60) --
	( 55.13, 85.60) --
	( 55.13, 89.53) --
	( 51.21, 89.53) --
	cycle;

\path[fill=fillColor] ( 55.02,107.05) --
	( 58.95,107.05) --
	( 58.95,110.97) --
	( 55.02,110.97) --
	cycle;
\definecolor{drawColor}{gray}{0.70}

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] (147.31, 72.23) --
	(151.13, 72.23) --
	(154.94, 72.23) --
	(158.76, 72.23) --
	(162.57, 72.23) --
	(166.39, 72.23) --
	(170.20, 72.23) --
	(174.02, 72.27) --
	(177.83, 72.70) --
	(181.65, 76.95) --
	(185.46, 89.66) --
	(189.28,106.37) --
	(193.09,123.35);
\definecolor{drawColor}{RGB}{217,95,2}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (147.31, 72.11) --
	(151.13, 72.11) --
	(154.94, 72.11) --
	(158.76, 72.11) --
	(162.57, 72.11) --
	(166.39, 72.11) --
	(170.20, 72.11) --
	(174.02, 72.15) --
	(177.83, 72.59) --
	(181.65, 76.89) --
	(185.46, 89.67) --
	(189.28,106.37) --
	(193.09,123.35);
\definecolor{drawColor}{RGB}{117,112,179}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (147.31, 84.74) --
	(151.13, 84.06) --
	(154.94, 83.93) --
	(158.76, 83.97) --
	(162.57, 84.20) --
	(166.39, 84.27) --
	(170.20, 84.38) --
	(174.02, 86.20) --
	(177.83, 93.38) --
	(181.65,111.72);
\definecolor{drawColor}{RGB}{231,41,138}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (147.31, 62.86) --
	(151.13, 60.69) --
	(154.94, 60.69) --
	(158.76, 60.69);
\definecolor{fillColor}{RGB}{117,112,179}

\path[fill=fillColor] (145.35, 82.78) --
	(149.28, 82.78) --
	(149.28, 86.70) --
	(145.35, 86.70) --
	cycle;

\path[fill=fillColor] (149.17, 82.10) --
	(153.09, 82.10) --
	(153.09, 86.02) --
	(149.17, 86.02) --
	cycle;

\path[fill=fillColor] (152.98, 81.97) --
	(156.91, 81.97) --
	(156.91, 85.90) --
	(152.98, 85.90) --
	cycle;

\path[fill=fillColor] (156.80, 82.01) --
	(160.72, 82.01) --
	(160.72, 85.93) --
	(156.80, 85.93) --
	cycle;

\path[fill=fillColor] (160.61, 82.23) --
	(164.54, 82.23) --
	(164.54, 86.16) --
	(160.61, 86.16) --
	cycle;

\path[fill=fillColor] (164.43, 82.30) --
	(168.35, 82.30) --
	(168.35, 86.23) --
	(164.43, 86.23) --
	cycle;

\path[fill=fillColor] (168.24, 82.41) --
	(172.16, 82.41) --
	(172.16, 86.34) --
	(168.24, 86.34) --
	cycle;

\path[fill=fillColor] (172.05, 84.24) --
	(175.98, 84.24) --
	(175.98, 88.16) --
	(172.05, 88.16) --
	cycle;

\path[fill=fillColor] (175.87, 91.42) --
	(179.79, 91.42) --
	(179.79, 95.34) --
	(175.87, 95.34) --
	cycle;

\path[fill=fillColor] (179.68,109.76) --
	(183.61,109.76) --
	(183.61,113.68) --
	(179.68,113.68) --
	cycle;
\definecolor{fillColor}{RGB}{217,95,2}

\path[fill=fillColor] (147.31, 75.16) --
	(149.96, 70.58) --
	(144.67, 70.58) --
	cycle;

\path[fill=fillColor] (151.13, 75.16) --
	(153.77, 70.58) --
	(148.49, 70.58) --
	cycle;

\path[fill=fillColor] (154.94, 75.16) --
	(157.59, 70.58) --
	(152.30, 70.58) --
	cycle;

\path[fill=fillColor] (158.76, 75.16) --
	(161.40, 70.58) --
	(156.12, 70.58) --
	cycle;

\path[fill=fillColor] (162.57, 75.16) --
	(165.22, 70.58) --
	(159.93, 70.58) --
	cycle;

\path[fill=fillColor] (166.39, 75.16) --
	(169.03, 70.58) --
	(163.75, 70.58) --
	cycle;

\path[fill=fillColor] (170.20, 75.16) --
	(172.84, 70.58) --
	(167.56, 70.58) --
	cycle;

\path[fill=fillColor] (174.02, 75.20) --
	(176.66, 70.62) --
	(171.37, 70.62) --
	cycle;

\path[fill=fillColor] (177.83, 75.64) --
	(180.47, 71.06) --
	(175.19, 71.06) --
	cycle;

\path[fill=fillColor] (181.65, 79.94) --
	(184.29, 75.37) --
	(179.00, 75.37) --
	cycle;

\path[fill=fillColor] (185.46, 92.72) --
	(188.10, 88.15) --
	(182.82, 88.15) --
	cycle;

\path[fill=fillColor] (189.28,109.42) --
	(191.92,104.84) --
	(186.63,104.84) --
	cycle;

\path[fill=fillColor] (193.09,126.40) --
	(195.73,121.82) --
	(190.45,121.82) --
	cycle;

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (144.54, 62.86) -- (150.09, 62.86);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (147.31, 60.09) -- (147.31, 65.64);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (148.35, 60.69) -- (153.90, 60.69);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (151.13, 57.92) -- (151.13, 63.47);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (152.17, 60.69) -- (157.72, 60.69);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (154.94, 57.92) -- (154.94, 63.47);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (155.98, 60.69) -- (161.53, 60.69);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (158.76, 57.92) -- (158.76, 63.47);
\definecolor{fillColor}{RGB}{27,158,119}

\path[fill=fillColor] (147.31, 72.23) circle (  1.96);

\path[fill=fillColor] (151.13, 72.23) circle (  1.96);

\path[fill=fillColor] (154.94, 72.23) circle (  1.96);

\path[fill=fillColor] (158.76, 72.23) circle (  1.96);

\path[fill=fillColor] (162.57, 72.23) circle (  1.96);

\path[fill=fillColor] (166.39, 72.23) circle (  1.96);

\path[fill=fillColor] (170.20, 72.23) circle (  1.96);

\path[fill=fillColor] (174.02, 72.27) circle (  1.96);

\path[fill=fillColor] (177.83, 72.70) circle (  1.96);

\path[fill=fillColor] (181.65, 76.95) circle (  1.96);

\path[fill=fillColor] (185.46, 89.66) circle (  1.96);

\path[fill=fillColor] (189.28,106.37) circle (  1.96);

\path[fill=fillColor] (193.09,123.35) circle (  1.96);
\definecolor{drawColor}{gray}{0.70}

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] (256.72, 73.16) --
	(260.53, 73.16) --
	(264.35, 73.16) --
	(268.16, 73.16) --
	(271.97, 73.16) --
	(275.79, 73.16) --
	(279.60, 73.16) --
	(283.42, 73.16) --
	(287.23, 73.16) --
	(291.05, 73.16) --
	(294.86, 73.16) --
	(298.68, 73.16) --
	(302.49, 73.17) --
	(306.31, 73.17) --
	(310.12, 73.20) --
	(313.94, 73.25) --
	(317.75, 73.38) --
	(321.56, 73.71) --
	(325.38, 74.42) --
	(329.19, 76.07) --
	(333.01, 78.80) --
	(336.82, 82.57) --
	(340.64, 87.78) --
	(344.45, 94.24) --
	(348.27,100.04) --
	(352.08,106.25);
\definecolor{drawColor}{RGB}{217,95,2}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (256.72, 72.63) --
	(260.53, 72.63) --
	(264.35, 72.63) --
	(268.16, 72.63) --
	(271.97, 72.63) --
	(275.79, 72.63) --
	(279.60, 72.63) --
	(283.42, 72.63) --
	(287.23, 72.63) --
	(291.05, 72.63) --
	(294.86, 72.63) --
	(298.68, 72.63) --
	(302.49, 72.64) --
	(306.31, 72.64) --
	(310.12, 72.67) --
	(313.94, 72.73) --
	(317.75, 72.87) --
	(321.56, 73.21) --
	(325.38, 73.96) --
	(329.19, 75.58) --
	(333.01, 78.49) --
	(336.82, 82.32) --
	(340.64, 87.62) --
	(344.45, 94.08) --
	(348.27, 99.98) --
	(352.08,106.31);
\definecolor{drawColor}{RGB}{117,112,179}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (256.72, 85.43) --
	(260.53, 83.72) --
	(264.35, 83.89) --
	(268.16, 83.69) --
	(271.97, 85.93) --
	(275.79,108.62);
\definecolor{drawColor}{RGB}{231,41,138}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (256.72, 61.86) --
	(260.53, 61.00) --
	(264.35, 61.00) --
	(268.16, 61.00) --
	(271.97, 61.00) --
	(275.79, 61.15) --
	(279.60, 61.15);
\definecolor{fillColor}{RGB}{27,158,119}

\path[fill=fillColor] (256.72, 73.16) circle (  1.96);

\path[fill=fillColor] (260.53, 73.16) circle (  1.96);

\path[fill=fillColor] (264.35, 73.16) circle (  1.96);

\path[fill=fillColor] (268.16, 73.16) circle (  1.96);

\path[fill=fillColor] (271.97, 73.16) circle (  1.96);

\path[fill=fillColor] (275.79, 73.16) circle (  1.96);

\path[fill=fillColor] (279.60, 73.16) circle (  1.96);

\path[fill=fillColor] (283.42, 73.16) circle (  1.96);

\path[fill=fillColor] (287.23, 73.16) circle (  1.96);

\path[fill=fillColor] (291.05, 73.16) circle (  1.96);

\path[fill=fillColor] (294.86, 73.16) circle (  1.96);

\path[fill=fillColor] (298.68, 73.16) circle (  1.96);

\path[fill=fillColor] (302.49, 73.17) circle (  1.96);

\path[fill=fillColor] (306.31, 73.17) circle (  1.96);

\path[fill=fillColor] (310.12, 73.20) circle (  1.96);

\path[fill=fillColor] (313.94, 73.25) circle (  1.96);

\path[fill=fillColor] (317.75, 73.38) circle (  1.96);

\path[fill=fillColor] (321.56, 73.71) circle (  1.96);

\path[fill=fillColor] (325.38, 74.42) circle (  1.96);

\path[fill=fillColor] (329.19, 76.07) circle (  1.96);

\path[fill=fillColor] (333.01, 78.80) circle (  1.96);

\path[fill=fillColor] (336.82, 82.57) circle (  1.96);

\path[fill=fillColor] (340.64, 87.78) circle (  1.96);

\path[fill=fillColor] (344.45, 94.24) circle (  1.96);

\path[fill=fillColor] (348.27,100.04) circle (  1.96);

\path[fill=fillColor] (352.08,106.25) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (253.94, 61.86) -- (259.49, 61.86);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (256.72, 59.08) -- (256.72, 64.63);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (257.76, 61.00) -- (263.31, 61.00);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (260.53, 58.23) -- (260.53, 63.78);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (261.57, 61.00) -- (267.12, 61.00);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.35, 58.23) -- (264.35, 63.78);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (265.39, 61.00) -- (270.94, 61.00);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (268.16, 58.23) -- (268.16, 63.78);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (269.20, 61.00) -- (274.75, 61.00);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (271.97, 58.23) -- (271.97, 63.78);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (273.01, 61.15) -- (278.56, 61.15);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (275.79, 58.38) -- (275.79, 63.93);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (276.83, 61.15) -- (282.38, 61.15);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (279.60, 58.38) -- (279.60, 63.93);
\definecolor{fillColor}{RGB}{117,112,179}

\path[fill=fillColor] (254.75, 83.46) --
	(258.68, 83.46) --
	(258.68, 87.39) --
	(254.75, 87.39) --
	cycle;
